On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-03-24 Manuscript/manuscript.tex
edits/comments on methods

\jy{turn on the column number mode of your editor. Keep the width to under 80.}

@@

Block bootstrap is a powerful tool for constructing confidence intervals when
making inferences about dependent data. Early ideas were developed
independently by \citet{hall1985resampling}, \citet{carlstein1986use}, and 
\citet{kunsch1989jackknife}.
It has since been applied in various fields such as econometrics
\citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
Block bootstrap is particularly useful for serially dependent
data when the serial dependence is not specified or not of primary interest.
The method is expected to produce confidence intervals with coverage rates
matching their nominal levels as the sample size grows to infinity. However,
when dealing with finite sample sizes, an important question is how large the
sample size needs to be for block bootstrap confidence intervals to have the
desired coverage rates.

The necessary sample size for bootstrap standard errors to provide valid
uncertainty measures in practice has not been extensively studied. For
independent data and non-block bootstrap, \citet{hesterberg2015teachers} notes
that while percentile-based confidence intervals from nonparametric bootstrap
are more accurate than $t$-intervals for larger sample sizes, they are
less accurate for smaller sample sizes. In the contect of structural equation
modeling, \citet{nevitt2001performance} find
that a sample size of 200--1000 is usually sufficient for interval estimation
using standard nonparametric bootstrap. For dependent data, the necessary sample
size for block bootstrap is even less clear. In a linear regression setting with
dependent data, \citet{goncalves2005bootstrap} find that, standard error
estimates from block bootstrap in small samples may be more accurate than
inference from closed-form asymptotic estimates, but block bootstrap percentile
confidence intervals still do not have sufficient coverage even for sample size
$n = 1024$.

The goal of this paper is to provide some practical recommendations on
necessary sample size for block bootstrap with dependent data. We consider a
simple situation of a stationary time series, where the parameters of
interests are the mean, standard deviation, and the first-order
autocorrelation coefficient. We compare three variants of block bootstrap
confidence intervals from the literature \citep{diciccio1996bootstrap,
  rice2006mathematical}: a basic percentile interval, a percentile
interval centered around the estimate, and a bias-corrected and
accelerated ($BC_a$) interval also centered around the original estimate. Their
empirical coverage rates at different sample sizes and dependence levels are
compared in a simulation study. The results of this study suggest that
appropriate recovery of temporal dependence parameters is heavily dependent on
the type of interval used.

The remainder of the papers is organized as follows:
The Block Bootstrap Confidence Intervals section reviews how these intervals
are constructed as well as the general procedure for block bootstrap parameter
estimation. The Simulation Study section offers an explanation of the
simulation design and results. Finally, the Concluding Remarks section
discusses the main takeaways from the results, how these findings could be
useful, and possible future explorations.

\section{Block Bootstrap Confidence Intervals}
\label{sec:blkbootreview}

Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$.
Our goal is to construct a confidence intervals for a parameter $\theta$ in the
data generating model of the series. Suppose that $\hat\theta_n$ is a point
estimator of~$\theta$ based on the observed series. Bootstrap is a powerful
approach to construct confidence intervals. If the observations in the series
were independent, a standard nonparametric bootstrap procedure would draw a
large number~$B$ bootstrap copies of the observed data, and calculate an
estimate $\hat\theta_n^{(b)}$ for each copy $b = 1, \ldots, B$. The uncertainty
of $\hat\theta_n$ is then estimated by the empirical uncertainty of the
$\hat\theta_n^{(b)}$'s. When serial dependence is present, the bootstrap
procedure needs to preserve the serial dependence. Block bootstrap was
motivated for this situation.

\subsection{Draw a Block Bootstrap Sample}

\jy{Paragraph: describe how to construct one non-overlapping block bootstrap
  sample.}

The designer of the study can choose whether the blocks overlap or not. If the
blocks do not overlap, it is called non-overlapping or non-moving block
bootstrap. In this case, blocks are resample randomly from the set of all
non-overlapping blocks of size $l$. For non-moving block bootstrap, $l \vert n$
must always be true. In this case, a set of $n / l$ non-overlapping blocks of
size $l$ is constructed from the original sample. The set would take the form:
$\{[X_1, ..., X_l], [X_{l+1}, ..., X_{2l}], ..., [X_{n-l+1}, X_n]\}$. Each
bootstrapped pseudo-sample is created by sampling $n / l$ blocks with
replacement from the same set.

\jy{Paragraph: describe how to construct one overlapping block bootstrap.}

If the blocks do overlap, it is called overlapping or moving block bootstrap.
In this case, blocks are resampled randomly from the set of all possible
blocks of size $l$. For moving block bootstrap, $l \vert n$ is not a necessary
condition. The set of available blocks is created by iterating through each
observation $i$ in the original sample and adding to the set the block of size
$l$ that begins with $i$. This set can limited to blocks that end with an
$i <= n$, meaning that $n - l + 1$ blocks are available to resample from. This
set takes the form:
$\{[X_1, ..., X_l], [X_2, ..., X_{l+1}], ..., [X_{n-l+1}, X_n]\}$. 
The set can also include blocks that ``wrap around'': in
other words, blocks that end with a lesser index than the index they began
with, meaning that $n$ blocks are available to resample from. This set takes
the form:
$\{[X_1, ..., X_l], [X_2, ..., X_{l+1}], ..., [X_n, X_{l-1}]\}$.
If $l \vert n$,
a bootstrapped pseudo-sample is created by taking a sample of $n / l$ blocks
from the set with replacement to create a new pseudo-sample of size $n$. If
$l does not divide n$, the last block selected will be reduced in size so that
the final size of the pseudo-sample is $n$. Moving block bootstrap was used in
this study as it has been found to yield the lowest error in general
\citep{radovanov2014comparison}. The larger set of available blocks was used.

\jy{Paragraph: comment on selection block size;
  mention that the two procedures are both valid with similar performance (cite
  references to support the claim).}

The block should be of size $l$ large enough for each
pseudo-sample to exhibit some temporal dependence, yet small enough for there
to be some variability between each pseudo-sample. Ideally, as $n$ increases,
$l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
often assigned a value as a function of $n$. A common function that is
considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
\citep{buhlmann1999block}.

\subsection{Construct Confidence Intervals}

Suppose that we have repeated the steps in the last subsection $B$ times, and
that for $b \in \{1, \ldots, B\}$, we have obtained an estimator
$\hat\theta_n^{(b)}$ based on the $b$th bootstrap sample using the same method
that was applied to $\{X_t: t = 1, \ldots, n\}$ to obtain $\hat\theta_n$.
Now the question is, how to construct confidence intervals for $\theta$
using the $B$ bootstrap point estimates
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$.

\jy{Paragraph: basic percentiles; use the terminologies in the literature.}

In this study, 1000 $\hat\theta_n^{(b)}$ were created for one simulation of
block bootstrap estimation. Using this distribution of $\hat\theta_n^{(b)}$,
several variants of a $1 - \alpha$/2 \% confidence interval for the parameter
can be constructed. The most simplistic method for constructing this interval
is the basic percentile confidence interval. For a parameter $\theta$, the
percentile $1 - \alpha$/2 \% confidence interval takes the form:
\[ [\hat\theta_{n, \alpha/2}^{(b)}, \hat\theta_{n, 1 - \alpha/2}^{(b)}].\]

This interval works well when attempting to recover the mean and
standard deviation of a temporally dependent process, but its coverage of
the temporal dependence deteriorates as $n$ increases.

\jy{Paragraph: centered.}

A potential solution to
this issue is to center the intervals around $\hat{\theta}_{n}$. To do this,
the distribution of $\delta^*$ should be considered. For a parameter $\theta$,
the $\hat{\theta}_{n}$-centered $1 - \alpha$/2 \% confidence interval takes
the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha/2},
  \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\]

\jy{Paragraph: BCa}

An alternative method is a $BC_a$ interval centered around $\hat{\theta}_{n}$.
For a parameter $\theta$, the $BC_a$ $1 - \alpha$/2 \% confidence interval
takes the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha_1},
  \hat{\theta}_{n} + \delta^*_{\alpha_2}].\]
$\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and
$z_{2}$, respectively, where:
\[z_{1} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} +
z_{0}\] and
\[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} +
z_{0}.\]
Where $z_0$ is the quantile function of the proportion of
$\hat\theta_n^{(b)} < \bar\theta_n^{(b)}$, and $a$ is the skewness (computed
using
the skewness function from the R e1071 package \citep{e1071}) of
$\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the
original sample computed without the $i^{th}$ block.

Thus, there are three types of intervals that can be constructed for block
bootstrap estimation in this study: Percentile, $\hat{\theta}_{n}$-Centered,
and $BC_a$.

@@

We designed a simulation study to compare the performance of the different
block
bootstrap confidence intervals. In particular, we generated time series $X_t$
from a 1st order auto-regressive (AR1) process:
\[
X_t = \phi X_{t-1} + \epsilon_t,
\]
where $\phi$ is an auto-regressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$.
The series $X_t$ has mean zero and variance
$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$,
we
set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x^2 = 1$, the variance of $X_t$; and
2) $\phi$, the lag-1 auto-correlation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, \ldots, 1000\}$. In each configuration, we generated 1000
replicates. For each replicate, we constructed three 95\% block bootstrap
confidence intervals for each parameter as described in the last section, and
estimated their actual coverage rates along with their 95\% confidence
intervals from the 1000 replicates. The block bootstrap sampling step was done
with function \texttt{tsboot} from R package \textsl{boot} \citep{boot}, with
block size $\lceil n / l \rceil$. This function by default is an implementation
of moving block bootstrap as described in the previous section.
\jy{size? also it was overlapping blocks. Describe the details here.}
The results are graphically displayed in Figures~\ref{fig:mu}--\ref{fig:phi};
these figures were generated using the using
the R ggplot2 package \citep{ggplot2}.

Each interval either recovers $\theta$ or does not. Remember that
95\% of many of a certain type of 95\% confidence intervals constructed from
samples of the same $n$ should recover $\theta$. To see if this is
approximately the case, one can run 1000 replications of the block bootstrap
procedure, and for each interval-$\theta$ pair, the rate at which that type of
interval recovers $\theta$ can be recorded. The coverage rate is, of course, a
point estimate of a proportion, so a 95\% confidence interval of this coverage
proportion (with $n_{CI} = 1000$) can be constructed, and if the proportion
.95 is included in the interval, the block bootstrap method is likely working
well. If all values in the interval are below .95, the results suggest that the
method either is providing an inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

@@

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_mu}
  \caption{Plots of $\mu$ coverage rates for each interval type and $\phi$
    combination. The orange dotted line represents the 95\% nominal coverage
    rate. The error bars represent a 95\% confidence interval for the coverage
    proportion out of 1000 replications for each $n$. Results from $n$
    ranging from 100-700 were recorded.}
  \label{fig:mu}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_sigma}
  \caption{Plots of $\sigma$ coverage rates for each interval type and $\phi$
    combination. The orange dotted line represents the 95\% nominal coverage
    rate. The error bars represent a 95\% confidence interval for the coverage
    proportion out of 1000 replications for each $n$. Results from $n$
    ranging from 100-700 were recorded.}
  \label{fig:sigma}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_phi}
  \caption{Plots of $\phi$ coverage rates for each interval type and $\phi$
    combination. The orange dotted line represents the 95\% nominal coverage
    rate. The error bars represent a 95\% confidence interval for the coverage
    proportion out of 1000 replications for each $n$. Results from $n$
    ranging from 100-700 were recorded.}
  \label{fig:phi}
\end{figure}

>>>>

@@

Block bootstrap is a powerful tool for constructing confidence intervals (CI)
when making inferences about dependent data. Early ideas were developed
independently by \citet{hall1985resampling}, \citet{carlstein1986use}, and 
\citet{kunsch1989jackknife}.
It has since been applied in various fields such as econometrics
\citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
Block bootstrap is particularly useful for serially dependent
data when the serial dependence is not specified or not of primary interest.
The method is expected to produce CIs with coverage rates
matching their nominal levels as the sample size grows to infinity. However,
when dealing with finite sample sizes, an important question is how large the
sample size needs to be for block bootstrap CIs to have the
desired coverage rates.

The necessary sample size for bootstrap standard errors to provide valid
uncertainty measures in practice has not been extensively studied. For
independent data and non-block bootstrap, \citet{hesterberg2015teachers} notes
that while percentile-based CIs from nonparametric bootstrap
are more accurate than $t$-intervals for larger sample sizes, they are
less accurate for smaller sample sizes. In the contect of structural equation
modeling, \citet{nevitt2001performance} find
that a sample size of 200--1000 is usually sufficient for interval estimation
using standard nonparametric bootstrap. For dependent data, the necessary sample
size for block bootstrap is even less clear. In a linear regression setting with
dependent data, \citet{goncalves2005bootstrap} find that, standard error
estimates from block bootstrap in small samples may be more accurate than
inference from closed-form asymptotic estimates, but block bootstrap percentile
CIs still do not have sufficient coverage even for sample size
$n = 1024$.

The goal of this paper is to provide some practical recommendations on
necessary sample size for block bootstrap with dependent data. We consider a
simple situation of a stationary time series, where the parameters of
interests are the mean, standard deviation, and the first-order
autocorrelation coefficient. We compare three variants of block bootstrap
CIs from the literature \citep{diciccio1996bootstrap,
  rice2006mathematical}: a basic percentile interval, a percentile
interval centered around the estimate, and a bias-corrected and
accelerated ($BC_a$) interval also centered around the original estimate. Their
empirical coverage rates at different sample sizes and dependence levels are
compared in a simulation study. The results of this study suggest that
appropriate recovery of temporal dependence parameters is heavily dependent on
the type of interval used.

The remainder of the papers is organized as follows:
The Block Bootstrap CIs section reviews how these intervals
are constructed as well as the general procedure for block bootstrap parameter
estimation. The Simulation Study section offers an explanation of the
simulation design and results. Finally, the Concluding Remarks section
discusses the main takeaways from the results, how these findings could be
useful, and possible future explorations.

\section{Block Bootstrap CIs}
\label{sec:blkbootreview}

Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$.
Our goal is to construct a CIs for a parameter $\theta$ in the
data generating model of the series. Suppose that $\hat\theta_n$ is a point
estimator of~$\theta$ based on the observed series. Bootstrap is a powerful
approach to construct CIs. If the observations in the series
were independent, a standard nonparametric bootstrap procedure would draw a
large number~$B$ bootstrap copies of the observed data, and calculate an
estimate $\hat\theta_n^{(b)}$ for each copy $b = 1, \ldots, B$. The uncertainty
of $\hat\theta_n$ is then estimated by the empirical uncertainty of the
$\hat\theta_n^{(b)}$'s. When serial dependence is present, the bootstrap
procedure needs to preserve the serial dependence. Block bootstrap was
motivated for this situation.

\subsection{Block Bootstrap Sample}

Block bootstrap preserves the serial dependence in the observed data by
partitioning the data into blocks and perform bootstrap on the blocks.
In particular, consider block size~$l$ and, for convenience, suppose that
$n$ is a multiple of $l$ such that there are $k = n / l$ blocks. Each block~$j$
is $Y_j = \{X_{(j - 1) * l + 1}, \ldots, X_{(j - 1) * l + l}\}$,
$j = 1, \ldots,   k$.  Then, we sample $k$ blocks of $Y_j$'s from the set 
$\{Y_1, \ldots, Y_k\}$ with replacement and concatenate the $k$ sampled blocks
in the order they are picked to form a bootstrap sample of the data. The
formation of the bootstrap sample ensures that the between-block dependence is
week and that the within-block serial dependence is preserved. Because the
blocks here are non-overlapping, this bootstrap approach is known as
non-overlapping block bootstrap, or simple block bootstrap.

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
$j = 1, \ldots, n - b + 1$. Now we draw $k$ blocks from the $(n - b + 1)$ blocks
of $Z_j$'s with replacement and then aligning them in the order they were picked
to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
block selected will be reduced in size so that the final size of the
block bootstrap sample is $n$. Moving block bootstrap was used in
this study as it has been found to yield the lowest error in general
\citep{radovanov2014comparison}. The larger set of available blocks was used.
\jy{what does the last sentence mean?}

The block size~$l$ needs to chosen with care. It needs to be large enough for
each bootstrap sample to preserve the serial dependence, yet small enough for
there to be some variability between each bootstrap sample. As $n$ increases,
$l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
often assigned a value as a function of $n$. A common function that is
considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
\citep{buhlmann1999block}.

\subsection{Construct CIs}

Suppose that we have repeated the steps in the last subsection $B$ times, and
that for $b \in \{1, \ldots, B\}$, we have obtained an estimator
$\hat\theta_n^{(b)}$ based on the $b$th bootstrap sample using the same method
that was applied to $\{X_t: t = 1, \ldots, n\}$ to obtain $\hat\theta_n$.
Now the question is, how to construct CIs for $\theta$
using the $B$ bootstrap point estimates
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$.
We consider three kinds of CIs.

\paragraph{Percentile CI}
Let $\hat\theta_{n, B, \alpha}$ be the empirical $100\alpha$th percentile of
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)$
empirical percentile CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)}, \hat\theta_{n, 1 - \alpha/2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$.
%% Not the right place
%% This interval works well when attempting to recover the mean and
%% standard deviation of a temporally dependent process, but its coverage of
%% the temporal dependence deteriorates as $n$ increases.

\paragraph{Centered Percentile CI}
Centered percentile CI is centered at the point estimator and uses the variation
in the bootstrap estimates to construct the error bound. A $(1 - \alpha)$ CI is
\[
(\hat{\theta}_{n} + \delta^*_{\alpha/2},
\hat{\theta}_{n} + \delta^*_{1 - \alpha/2}).
\]
\jy{Define $\delta^*$?}
\jy{Say a few words about its properties}

\paragraph{Bias Corrected and Accelerated (BCA) Bootstrap CI}
The $1 - \alpha$ \% BCA CI takes the form:
\[
(\hat{\theta}_{n} + \delta^*_{\alpha_1},
\hat{\theta}_{n} + \delta^*_{\alpha_2}),
\]
\jy{Not clear and not flowing well. Restructure the writing. Practice my writing tips.}
where $\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and
$z_{2}$, respectively, where:
\[z_{1} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} +
z_{0}\] and
\[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} +
z_{0}.\]
Where $z_0$ is the quantile function of the proportion of
$\hat\theta_n^{(b)} < \bar\theta_n^{(b)}$, and $a$ is the skewness (computed
using
the skewness function from the R e1071 package \citep{e1071}) of
$\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the
original sample computed without the $i^{th}$ block.
\jy{Say a few words about its properties.}

@@

We designed a simulation study to compare the performance of the different
block
bootstrap CIs. In particular, we generated time series $X_t$
from a 1st order auto-regressive (AR1) process:
\[
X_t = \phi X_{t-1} + \epsilon_t,
\]
where $\phi$ is an auto-regressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$.
The series $X_t$ has mean zero and variance
$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$,
we
set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x^2 = 1$, the variance of $X_t$; and
2) $\phi$, the lag-1 auto-correlation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, \ldots, 1000\}$. In each configuration, we generated 1000
replicates. For each replicate, we constructed three 95\% block bootstrap
CIs for each parameter as described in the last section, and
estimated their actual coverage rates along with their 95\% confidence
intervals from the 1000 replicates. The block bootstrap sampling step was done
with function \texttt{tsboot} from R package \textsl{boot} \citep{boot}, with
block size $\lceil n / l \rceil$. This function by default is an implementation
of moving block bootstrap as described in the previous section.
\jy{size? also it was overlapping blocks. Describe the details here.}

\jy{Explain what metric was used to compare their performances. That is, the
  coverage rates and how it was calculated. If a CI is valid, then the coverages
  rate is expected to match its nominal level.}

\jy{Make it flow better and conciser}
Each interval either recovers $\theta$ or does not. Remember that
95\% of many of a certain type of 95\% CIs constructed from
samples of the same $n$ should recover $\theta$. To see if this is
approximately the case, one can run 1000 replications of the block bootstrap
procedure, and for each interval-$\theta$ pair, the rate at which that type of
interval recovers $\theta$ can be recorded. The coverage rate is, of course, a
point estimate of a proportion, so a 95\% CI of this coverage
proportion (with $n_{CI} = 1000$) can be constructed, and if the proportion
.95 is included in the interval, the block bootstrap method is likely working
well. If all values in the interval are below .95, the results suggest that the
method either is providing an inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

@@

The results are graphically displayed in Figures~\ref{fig:mu}--\ref{fig:phi};
these figures were generated using the using
the R ggplot2 package \citep{ggplot2}.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_mu}
  \caption{Plots of $\mu$ coverage rates for each interval type and $\phi$
    combination. The orange dotted line represents the 95\% nominal coverage
    rate. The error bars represent a 95\% CI for the coverage
    proportion out of 1000 replications for each $n$. Results from $n$
    ranging from 100-700 were recorded.}
  \label{fig:mu}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_sigma}
  \caption{Plots of $\sigma$ coverage rates for each interval type and $\phi$
    combination. The orange dotted line represents the 95\% nominal coverage
    rate. The error bars represent a 95\% CI for the coverage
    proportion out of 1000 replications for each $n$. Results from $n$
    ranging from 100-700 were recorded.}
  \label{fig:sigma}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_phi}
  \caption{Plots of $\phi$ coverage rates for each interval type and $\phi$
    combination. The orange dotted line represents the 95\% nominal coverage
    rate. The error bars represent a 95\% CI for the coverage
    proportion out of 1000 replications for each $n$. Results from $n$
    ranging from 100-700 were recorded.}
  \label{fig:phi}
\end{figure}
